\documentclass{cv}
\usepackage[utf8]{inputenc}

\title{cv}
\setname{SEOJUNE LEE}
\setaltname{이서준}
\setmail{leeseojune@snu.ac.kr}
% \setphone{(+82) 10-7643-2441}
\sethomepage{https://seojune.site/}

\usepackage[hidelinks]{hyperref} % remove color from links

\begin{document}

\cvheader

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \cvlargeline{Academic Interests}{Biomedical Imaging, Deep Learning}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Education}

\cventry{Seoul National University}{Seoul, Korea}
{Undergraduate Student}{Mar. 2021 - Present}
{
    \item \href{http://ece.snu.ac.kr/en}{Department of Electrical and Computer Engineering}
    \item 1.5-year absence due to military service (Mar. 2023 - Sep. 2024)
    \item GPA: 4.24/4.3
}
\cventry{\href{http://ksa.hs.kr/}{Korea Science Academy of KAIST}}{Busan, Korea}
{High School}{Feb. 2018 - Feb. 2021}
{
    \item Science-centric magnet high school affiliated with KAIST
    \item GPA: 4.17/4.3 (Rank: 4/131)
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% RESEARCH PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experiences}

\cventry{Machine Perception and Reasoning Laboratory, SNU}{Seoul, Korea}
{Undergraduate Research Intern}{Sep. 2024 - Present}
{
    \item Advisor: Prof. Jonghyun Choi
}

\cventry{Ministry of National Defense}{Seongnam, Gyeonggi, Korea}
{Military Software Engineer, Sergeant}{Mar. 2023 - Sep. 2024}
{
    \item Mandatory military service. Developed a web-based signal processing program as a full-stack developer
    \item Used a tech stack that includes React.js and Django. Specific details remain classified.
}
\cventry{Laboratory of Imaging Science and Technology (LIST), SNU}{Seoul, Korea}
{Undergraduate Research Intern}{Jun. 2022 - Aug. 2022}
{
    \item Advisor: Prof. Jongho Lee
    \item Studied deep learning-based approaches to correct motion artifacts in MR(magnetic resonance) images
    \item Devised methods for simulating images with motion artifacts and trained ResNets on them
}
\begin{comment}
\cventry{Research \& Education Program (R\&E)}{Korea Science Academy}
{Title: On Wave Propagation in Hyperhelix Structures}{Mar. 2019 - Dec. 2019}
{
    \item Advised by Dr. Yongdeok Kim
    \item Implemented a mechanical wave simulator for curved waveguide using python %\href{https://research.ksa.hs.kr/2019RNE_MAT02}{[paper]}
    \item Gave a poster presentation at International Science Youth Forum (ISYF) @ Singapore 2020
}
\end{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% HONORS & SCHOLARSHIPS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Honors \& Scholarships}
\cvhonor{\textbf{The National Scholarship for Science and Engineering}, \textit{Korea Student Aid Foundation} (full tuition)}{2021}
\cvhonor{\textbf{Hanseong Nobel Scholarship for the Gifted}, \textit{Hanseong Sonjaehan Foundation} (\$10000 equivalent)} {2018}
\cvhonor{Bronze Prize in \textbf{Korea Olympiads in Informatics}, \textit{Ministry of Science and ICT}}{2018}


\vspace{-4mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Skills}
\cvline{Programming}{Python, C++, CUDA, Verilog, JavaScript, Rust}
\cvline{Frameworks}{PyTorch, Hugging Face, Django, React.js}
\cvline{Tools}{Git, \LaTeX{}}
\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% EXTRACURRICULAR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \cvsection{Extracurricular Activities}
% \cventry{\href{https://www.linkedin.com/company/outta아우타/}{OUTTA}}{Mar. 2022 - Aug. 2022}
% {Student Mentor}{}
% {
%     \item Organized online deep learning bootcamp, gave lectures on natural language processing
% }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% MISCELLANIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Miscellanies}
\cvline{English}{\hspace{-15mm}TOEFL iBT: 109/120(R30/L27/S23/W29), TOEIC: 970/990 (expired)}
\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Relevant Coursework
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Relevant Coursework}
\cvlist{
    \item Mathematical Foundations of Deep Neural Networks, Computational Linguistics
    \item Compuer Organization, Scalable High-Performance Computing (\textit{graduate}), Systems Programming, Logic Design
    \item Intro. to Electromagnetism,  Signals \& Systems, Circuit Theory, Control Engineering
    % \item Mathematical Analysis \href{https://drive.google.com/file/d/1yV9ByaC-haFajsSLHibLfft2XM5FeOrN/view?usp=drivesdk}{(self-studied)}
}

\vspace{3mm}
Last updated at: \today
\end{document}
